%% Supplement to "When Numerical Structure Reads the Recording Pipeline"
%% (lprofile_paper_v10_recording.tex). First standalone supplement source;
%% consolidates technical material previously in the main text (v9) plus the
%% exploratory Build geo15 detail. All frozen results unchanged; sources in
%% artifact/claim_manifest.csv and RESULT_PROVENANCE.md.
\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{natbib}   %% ASA author-date (JSSAM)
\setcitestyle{round,aysep={}}
\usepackage{url}

\newcommand{\keff}{k_{\mathrm{eff}}}
\newcommand{\rmass}{\rho}
\newcommand{\gdepth}{\tau}
\renewcommand{\thesection}{S\arabic{section}}
\renewcommand{\thetable}{S\arabic{table}}
\renewcommand{\thealgorithm}{S\arabic{algorithm}}
\renewcommand{\theequation}{S\arabic{equation}}

\title{Supplement to ``When Numerical Structure Reads the Recording Pipeline:
A Boundary for Factorization-Based Data Analysis''}
\author{}  %% BLINDED
\date{}

\begin{document}
\maketitle

\section{Definitions, invariances, and the coordinate algorithm}
\label{s:defs}

\paragraph{L-profile.}
For $n = \prod_{i=1}^r p_i^{a_i}$ with distinct primes $p_i$, the log-shares
are $\ell_j = a_{(j)} \ln p_{(j)} / \ln n$, sorted so
$\ell_1 \ge \cdots \ge \ell_r$, $\sum_j \ell_j = 1$. We read
$L_1 = \ell_1$, $L_2 = \ell_2$, $L_3 = \ell_3$,
$\mathrm{Tail} = \sum_{j \ge 3} \ell_j = 1 - \ell_1 - \ell_2$, and
$H_2 = \sum_j \ell_j^2$ (Simpson concentration of multiplicative energy).
Per-record quantities are averaged over a channel's records. The channel's effective
factor count is the ratio of averages
$\keff = \big(\sum_d w_d\, \mathbb{E}[H_2 \mid d]\big) / \overline{H_2}$,
with $w_d$ the channel's digit histogram,
$d(n) = \lfloor \log_{10} n \rfloor + 1$, and $\overline{H_2}$ the mean
record-level concentration---this (not an average of per-record ratios) is
what the analysis code computes, matching main-text Eq.~(2).
Records with fewer than three prime-power parts have $L_3 = 0$ structurally
(see \S\ref{s:geo15}).

\paragraph{What the profile retains of the primes.}
Every statistic of the sorted vector $(\ell_j)$ depends on $n$ only through
the multiset $\{a_i \ln p_i\}$: the profile discards prime \emph{names}
but retains prime \emph{magnitudes} through the $\ln p_i$. It is therefore
\emph{not} invariant under prime relabeling---replacing a prime by one of a
different size changes the profile ($6 = 2\cdot3$ has
$L_1 = \ln 3/\ln 6 \approx 0.613$; relabeling $3 \to 101$ gives
$202 = 2\cdot101$ with $L_1 \approx 0.870$). This is precisely why
small-prime composition can act as driver 3 of the main-text reduction: the
smallness of the grid primes is visible to the profile. The accurate
statement used throughout is that shape statistics are functionals of the
log-share multiset $\{a_i \ln p_i\}$---blind to prime names given their
sizes.

\paragraph{Scale invariance of the residual coordinates.}
Multiplying a field by $10^c$ (a units change) adds $c$ to both $v_2$ and
$v_5$ of every record, where $v_p$ is the $p$-adic valuation. The de-rounded
coordinates are computed on the $2\cdot5$-free core $n / (2^{v_2} 5^{v_5})$,
which is unchanged by the $10^c$ factor:
$2^{v_2(10^c n)} 5^{v_5(10^c n)} = 10^c \cdot 2^{v_2(n)} 5^{v_5(n)}$. All
scale-clean statistics are therefore exactly invariant under decimal unit
scaling. This invariance is what exposes the ``domain signal'' of the main
text \S4 as a units artifact: it reverses sign on monetary channels once the
coordinates are made scale-clean (the de-rounded second log-share residual: raw $dL_2$ $+0.042$ $\to$
scale-clean $dL_2'$ $-0.045$). The grid mass and grid depth are by design \emph{not}
scale-invariant---they are the units/grid readout---and are corrected against
the magnitude-matched null.

\paragraph{Recording-grid coordinates (main text \S3), full set.}
Grid mass $\rmass(n) = (v_2(n)\ln 2 + v_5(n)\ln 5)/\ln n$ with its
$c_2$/$c_5$ additive split; grid conformance
$\gamma = \frac1N \sum_k \mathbf{1}[g_0 \mid n_k]$ for the channel's modal
grid $g_0$; grid depth
$\gdepth(n) = \min(v_2(n), v_5(n)) = \max\{t : 10^t \mid n\}$; residue
quantization $Q_m = \frac12 \sum_{r=0}^{m-1}
|\widehat{\Pr}(n \equiv r \bmod m) - \frac1m|$ at
$m \in \{100, 25, 49, 47, 43\}$, each reported against a magnitude-matched
uniform-null expectation; and the digit-conditioned grid-mass split
$|\rmass_{\mathrm{lo}} - \rmass_{\mathrm{hi}}|$ across the channel's
median-digit split (a mixed-era flag). Algorithm~\ref{alg:enc} computes all
eleven channel-level coordinates in $O(N \log n_{\max})$ from stored integers
alone.

\begin{algorithm}[t]
\caption{Recording-grid coordinates of a channel (eleven values)}
\label{alg:enc}
\begin{algorithmic}[1]
\Require integers $n_1,\dots,n_N$; modal grid $g_0$; moduli $\mathcal{M}=\{100,25,49,47,43\}$
\State $\rmass,\gdepth,\gamma,c_2,c_5 \gets 0$; counts $C_m[\cdot]\gets 0$ for $m\in\mathcal{M}$
\For{$k=1$ to $N$}
  \State $a_2\gets v_2(n_k)$; $a_5\gets v_5(n_k)$; $L\gets\ln n_k$
  \State $c_2 \mathrel{+}= a_2\ln2/L$; $c_5 \mathrel{+}= a_5\ln5/L$; $\gdepth \mathrel{+}= \min(a_2,a_5)$
  \State \textbf{if} $g_0\mid n_k$ \textbf{then} $\gamma\mathrel{+}=1$
  \For{$m\in\mathcal{M}$} $C_m[n_k \bmod m]\mathrel{+}=1$ \EndFor
\EndFor
\State $\rmass\gets(c_2+c_5)/N$; normalize $\gdepth,\gamma,c_2,c_5$ by $N$
\For{$m\in\mathcal{M}$} $Q_m\gets \tfrac12\sum_{r}|C_m[r]/N - 1/m|$ \EndFor
\State $\bar d\gets\mathrm{median}_k\, d(n_k)$
\State $\rmass_{\mathrm{lo}},\rmass_{\mathrm{hi}}\gets$ mean $\rmass(n_k)$ over $d(n_k)\le\bar d$ and $>\bar d$
\State \Return $\big(\rmass,\gdepth,\gamma,c_2,c_5,\{Q_m\},|\rmass_{\mathrm{lo}}-\rmass_{\mathrm{hi}}|\big)$
\end{algorithmic}
\end{algorithm}

\section{Null construction and the core-magnitude baseline}
\label{s:nulls}

\paragraph{Magnitude-conditioned baseline.}
The reference tables $\mathbb{E}[\cdot \mid d]$ are built from $2\times10^5$
seeded uniform draws per digit stratum $d = 1..18$ (frozen seed 20260702),
factorized exactly. $\mathbb{E}[L_1 \mid d]$ falls from $0.952$ ($d{=}1$) to
$0.633$ ($d{=}18$); the Poisson--Dirichlet limit value is
$0.6243$~\citep{dickman1930,billingsley1972,kingman1975,arratia2000}.
Derived baselines exist for the de-rounded core (seed 20260703) and the
deep-stripped core (seed 20260706). Channel residuals weight the stratum
expectations by the channel's own digit histogram.

\paragraph{Core-magnitude re-indexing (the reference correction).}
Stripping primes $\le c$ from $n$ yields the deep core
$\kappa_c(n) = \prod_{p_i > c} p_i^{a_i}$. The naive reference compares the
core's profile to $\mathbb{E}[\cdot \mid d(n)]$, indexed by the
\emph{original} digit length. But rounded values carry more small-prime mass,
lose more magnitude when stripped, and have smaller cores---and smaller
integers are intrinsically more concentrated. The correct reference indexes by
the core's own magnitude: draw uniform integers over the original strata,
strip identically, tabulate $\mathbb{E}[\mathrm{Tail} \mid d_\kappa]$ against
the core digit length $d_\kappa$, and weight by the channel's normalized core
digit histogram (Algorithm~\ref{alg:reindex}). Under this reference the
surviving arm-domain concentration excess collapses from $-0.0184$ to
$-0.0001$ ($90\%$ family-bootstrap CI $[-0.0004, +0.0004]$); the
exponent-stacking mechanism check ($1.9\%$ of observational records versus
$100\%$ of genuine smooth products) confirms no real concentration mechanism
was present.

\begin{algorithm}[t]
\caption{Core-magnitude re-indexing}
\label{alg:reindex}
\begin{algorithmic}[1]
\Require channel values $\{n_k\}$; strip cut $c$ (here $7$); core-magnitude table $\mathbb{E}[\cdot\mid d_\kappa]$
\State build the table once: uniform draws over strata $1..18$, strip by $\kappa_c$, tabulate vs $d_\kappa$
\For{each $n_k$}: $\kappa\gets\kappa_c(n_k)$; \textbf{if} $\kappa=1$ \textbf{skip}; accumulate $\mathrm{Tail}_c \equiv \mathrm{Tail}(\kappa)$, $H_2(\kappa)$; bump $w[d_\kappa]$
\EndFor
\State \Return $d\mathrm{Tail}^{\mathrm{core}} = \overline{\mathrm{Tail}_c} - \sum_{d_\kappa} \tfrac{w[d_\kappa]}{\sum w}\,\mathbb{E}[\mathrm{Tail}\mid d_\kappa]$ and $\keff^{\mathrm{core}}$
\end{algorithmic}
\end{algorithm}

\paragraph{Local-flatness stress (v10.3, exploratory; seed 20260718).}
A simulation maps where the model's local-flatness assumption fails
(\path{stage25_flatness.py}, plan frozen in \path{run_config_flat25.json};
output \path{flat25_results.csv}).
Latent draws $x \sim \mathrm{Exp}(\mathrm{scale} = r\,g)$ recorded on grids
$g \in \{10, 100\}$: at curvature-to-grid ratio $r = 0.5$ the recorded
quotient is far from generic ($dL_1$ of the quotient $-0.18$, quotient
$\keff$ $1.34$, decimal-prime log-share $0.64$ against a $0.36$ generic
reference); deviations shrink monotonically to $|dL_1| \le 0.013$ and
$\keff$ within $0.02$ of $1$ for $r \ge 5$. A zero-inflated count case
(Poisson $\lambda = 30$, $60\%$ zeros, $g = 10$) shows the same
small-support bias ($dL_1$ $+0.048$, $\keff$ $0.94$). Under the frozen
$2\,\mathrm{SE}$ adequacy rule (severe at $N = 4\times10^4$: $2\,\mathrm{SE}
\approx 0.002$) only the $r = 5$, $g = 100$ cell passes exactly; the
practical reading is the magnitude ordering above. Direction of the induced
bias: a \emph{false} composite/grid signature (inflated $\keff$ and
decimal-prime mass), never a masked process signal. Named failure regimes:
narrow-support latents ($r \lesssim 2$), sparse zero-inflated counts on
coarse grids, and benchmarked estimates (the W12-1 mechanism of \S S6).

\section{Corpus construction and quarantine}
\label{s:corpus}

A \emph{channel} is one integer-valued column of one dataset: $\ge 99\%$ of
non-null entries integers, $\ge 100$ records, maximum $\ge 2$, deduplicated by
content fingerprint. Integerization is canonical: absolute values; missing and
non-integer entries dropped; $|n| \le 1$ excluded (no factorization); monetary
fields scaled to integer cents (round-half-to-even); values above $10^{18}$
logged and skipped. Channels group into dataset-families (one source lineage)
and domains (named process areas). A prospectively specified quarantine reduced a
provisional map of $462$ candidate families in $15$ domains to the frozen
corpus of $18{,}951$ channels, $367$ families, $18$ domains (the
quarantine's relabeling re-partitioned the $15$ provisional domain labels
into the $18$ frozen ones)
(${\sim}9.6\times10^8$ exact factorizations), reassigning mislabeled
generator families; the frozen manifest records the patch and hashes. Two
properties are load-bearing for scope: a few high-volume administrative
sources dominate channel counts (network telemetry, procurement, and census
are $>90\%$ of channels), and domain labels are heterogeneous ($18$) though
uneven. The deviation log (16 entries) records data losses and access changes
(e.g., deletion of unpacked archive snapshots; API key requirements).

\paragraph{Raw-map teardown numbers (main text \S4).}
Three-cluster structure in the family-level $(L_1, \mathrm{Tail})$ plane:
silhouette $0.719$; cluster survival after dividing out $2\cdot5$: Jaccard
$0.39$--$0.43$; scale-clean sign reversal of the monetary domain signal
($+0.042 \to -0.045$); intrinsic dimension of the cleaned space $1.16$
(TwoNN); residue-quantization negative controls: planted resonant families
score $0.051$--$0.167$ against planted generic $\approx 0.0056$
(${\sim}9$--$30\times$), observed channels median $0.020$, 95th percentile $0.439$.

\paragraph{Leave-one-source-out robustness (v10.3, exploratory; seed
20260716).} The four-driver arm sequence and the core-magnitude collapse
were rerun excluding network telemetry, procurement, or census wholesale,
and with equal-family weighting (\path{stage23_loso.py}, holds-rule frozen in
\path{run_config_loso23.json}; outputs \path{loso23_results.csv},
\path{loso23_family_counts.csv}).
Telemetry and census contribute no families to the frozen arm-domain set
(equity markets, seismology, real estate, procurement, food\_nutrition), so
their exclusion leaves the arm untouched by construction---the residual
claim never rested on them; procurement's exclusion removes $8$ of $166$ arm
families. Every variant satisfies the frozen rule: raw arm Tail excess
$+0.091$ to $+0.092$; de-rounded $-0.021$; deep-strip $-0.018$ to $-0.019$;
core-indexed $-0.0001$ to $-0.0002$ with all $90\%$ family-bootstrap CIs
containing $0$ (telemetry-excluded: $-0.0001$ $[-0.0004, +0.0004]$;
procurement-excluded: $-0.0002$ $[-0.0005, +0.0003]$). Per-variant
per-domain family counts accompany the output table.

\section{The L1/L3 geography disposition (Build geo15)}
\label{s:geo15}

This exploratory build (seed 20260715) resolves the previously unresolved question of what the L1/L3 Cartesian
geography means. Its analysis plan and disposition rule were frozen in
\texttt{run\_config\_geo15.json} before results were computed. No frozen
confirmatory rule covers it; the $\Delta\mathrm{AUC} \approx 0.05$ retention
threshold is a project-management rule. Full narrative:
\texttt{L1\_L3\_DISPOSITION.md}.

\paragraph{Observational level.}
Per-record L-profiles were never persisted by the frozen pipeline; the finest
stored grain is the channel. Analyses run at three levels: per-record
(stratified recompute: $153$ channels, $17$ domains, $9{,}199$ per-record
profiles), channel ($18{,}992$ stored channel profiles), and family ($462$; the blocking
unit).\footnote{Three related counts appear in this paper and are defined
here once. The frozen post-quarantine corpus has $18{,}951$ channels in $367$
families (the main-text headline). The stored channel-profile table was
computed on the pre-quarantine observational set of $18{,}992$ channels in
$408$ families: the frozen $18{,}951$/$367$ plus the $41$ quarantined
generator channels (one family each, all carrying the \texttt{unresolved}
domain label; these are distinct from the $159$ in-corpus
\texttt{unresolved} channels of main-text Table~1), which every geo15 model
excludes via the \texttt{unresolved}/synthetic-control filters. The $462$ figure is the
cardinality of the full frozen family label map (observational plus
synthetic-control families); grouped holdout blocks on the
\texttt{dataset\_family} column of that map, so no two channels of one
family ever cross a fold boundary, and after the exclusions the models see
the frozen observational families only. Main-text Figure~6 summarizes
family-level $\keff$ over the $367$ frozen-corpus families.}
$37.5\%$ of sampled records have fewer than three prime-power parts, so
per-record $L_3$ is a structural zero for over a third of records
(conditional mean when defined: $0.158$); channels dominated by such records
(mean parts $< 2.5$) are faceted separately in every display.

\paragraph{Block A: raw geography.}
Recomputed uniform-integer pseudo-channels match the frozen baseline within
$0.02$ at every stratum (machinery validation). Exact products of $2/3/4$
primes sit at $(L_1, L_3) = (0.51, 0.00) / (0.35, 0.32) / (0.28, 0.25)$;
additive controls at the baseline ($0.67, 0.08$); the same exact products
after one decimal rounding (grid $10/100/1000$) land at
$L_1$ $0.47$--$0.60$, $L_3$ $0.10$--$0.15$---inside the recorded band.

\paragraph{Block B: controlled geography.}
Control sequence at channel level (domains with $\ge 5$ families; synthetic
and unresolved channels excluded): raw $(L_1, L_3)$ $\to$ digit-length
residuals $\to$ de-rounded ($2\cdot5$-stripped) residuals $\to$
residue-conditioned residuals. Out-of-family domain separability of the 2-D
coordinates (GroupKFold by family, macro OVR AUC, family-bootstrap $90\%$
CI): $0.526\,[0.508, 0.543]$ raw; $0.422\,[0.298, 0.527]$;
$0.513\,[0.495, 0.526]$; $0.522\,[0.509, 0.531]$. Family-level silhouettes by
domain are negative at every stage (no domain islands). The recomputed
digit-length residual $dL_1$ matches the frozen stored value to $10^{-5}$.

\paragraph{Block C: held-out incremental information.}
Grouped holdout (GroupKFold, 5 folds, groups = dataset-family; never
record-level CV), gradient-boosting classifier, family-grouped bootstrap
(500) CIs. Table~\ref{tab:heldout}. $L_3$ beyond recording variables $+ L_1$: a small positive increment of
$+0.013$, below the pre-declared $0.05$ retention threshold (a project rule);
the binary count-vs-amount task is at $0.9999$ from recording variables
alone. Two calibration caveats are stated plainly. First, paired
family-bootstrap $90\%$ CIs (stage29, seed 20260722; one family resample
shared by both ladders per draw) quantify the deltas at the family grain:
$L_1$ beyond R $+0.009$ $[-0.006, +0.026]$; $L_3$ beyond R$+L_1$ $+0.013$
$[-0.011, +0.038]$---the interval includes $0$; full profile beyond R
$+0.035$ $[+0.004, +0.073]$, positive but below the threshold. Second, the incremental-$\Delta$AUC ladder
is \emph{uncalibrated for hidden-process signal}: the task-sensitivity
control of this section calibrates the design against \emph{recording}
differences only, so a small $\Delta$AUC bounds what these coordinates add
to this task, not what any conceivable process signal could produce.
Consequence (disposition rule 4): the manuscript makes no claim that L1/L3
topology is independently informative.

\begin{table}[t]
\centering
\caption{Held-out ladders (exploratory; domain task over the 12 domains with
$\ge5$ families; macro OVR AUC, family-grouped bootstrap $90\%$ CI). Source:
\texttt{geo15\_heldout\_auc.csv}.}
\label{tab:heldout}
\small
\begin{tabular}{lcccc}
\toprule
feature set & domain AUC & $90\%$ CI & $\Delta$ vs R & $\Delta$ vs R+$L_1$ \\
\midrule
R (recording variables) & 0.512 & [0.497, 0.528] & --- & --- \\
R $+ L_1$ & 0.522 & [0.512, 0.531] & $+0.009$ & --- \\
R $+ L_1 + L_3$ & 0.535 & [0.514, 0.554] & $+0.022$ & $+0.013$ \\
R $+$ full profile & 0.547 & [0.525, 0.566] & $+0.035$ & $+0.025$ \\
\midrule
count vs amount (binary) & \multicolumn{4}{l}{R alone $0.9999$; adding $L_1, L_3$ changes nothing} \\
\midrule
\multicolumn{5}{p{0.9\linewidth}}{\footnotesize Deltas before rounding:
$+0.0091$, $+0.0222$, $+0.0131$, $+0.0349$, $+0.0258$. Paired family-bootstrap
$90\%$ CIs for the deltas are given in the text below.} \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Task-sensitivity positive control (v10.3, exploratory; seed
20260717).} The transfer design itself is calibrated by a positive control
(\path{stage24_taskpos.py}, plan frozen in
\path{run_config_taskpos24.json}; outputs \path{taskpos24_calibration.csv},
\path{taskpos24_permutation.csv}, \path{taskpos24_s1_diagnostics.csv}). Synthetic pseudo-channels ($150$
families $\times 3$ channels $\times 600$ records) with class labels defined
by injected recording differences run through the \emph{identical}
family-grouped pipeline: AUC rises from $0.47$--$0.49$ at zero effect to
$0.67$/$0.81$ (raw/digit-residual coordinates) at a grid-mass shift of
$+0.020$, $0.99$ at $+0.066$, and $1.00$ at full-coverage grids; a
tick-$7$ treatment with near-zero grid-mass shift is read at $1.00$ through
the shape coordinates. A family-level label-permutation null centers on
$0.485$ (range $[0.39, 0.61]$ over $20$ draws; one draw marginally exceeded
the frozen $0.6$ bound and is reported as such). The design is therefore
sensitive to recording differences an order of magnitude smaller than what
would be needed to explain the real corpus's transfer AUC of $0.526$ as a
design failure. Diagnostics of the digit-residual stage's below-chance point
($0.422$, wide CI): GroupKFold with the corpus's extreme family-size skew
yields one fold with a single test family and class (macro-AUC undefined),
one fold $98\%$ dominated by a single class ($0.864$), and three balanced
folds at $0.497$--$0.509$---fold instability at near-zero signal, not
negative information.

\paragraph{Block D: mechanism stress.}
Per-record recompute under transforms on the same subsample. A three-factor
exact product moves from $(0.35, 0.32)$ to $(0.62, 0.10)$ under $n \to n{+}1$
(the 12-digit baseline point is $(0.64, 0.09)$); one grid rounding does the
same. Recorded channels move most when the grid itself is removed (mean
$|\Delta L_1|$: $+1$ shift $0.078$; de-round $0.159$; strip$\le7$
$0.238$)---the grid is where the shape mass lives. Subsample domain
separability from $(L_1, L_3)$: identity $0.624$, after $n{+}1$ $0.521$.

\section{Spike-in machinery, tiers, and full results}
\label{s:spikein}

Hosts: the six amount-kind channels (capped at $15{,}000$ records); eligible
records have $2\cdot5$-free core $\kappa \ge 300$. With $t_i = \log_{10}
\kappa_i$ the host record's core magnitude, the injected product $Q_i$ comes
from three tiers: \emph{(a) naive}---balanced two-factor products at the
host's marginal core-magnitude distribution, placed on the modal grid at
random positions; \emph{(b) magnitude-matched}---in place: $t = t_i$ and the
record's exact grid part is reused, so the mixture's (grid, magnitude) joint
is host-exact; \emph{(c) base-matched adversarial}---$Q_i = 3^{b_3} 7^{b_7}
R$ with $(b_3, b_7)$ drawn from the host's empirical deep-core joint and $R$ a
balanced two-factor product coprime to $210 = 2\cdot3\cdot5\cdot7$,
matching grid, magnitude,
\emph{and} the small-prime joint, leaving composite structure of the $>7$ core
as the only difference from a generic quotient.

Detection: a channel is recovered at mixture $f$ iff the replicate-median
$\keff^{\mathrm{core}}$ (15 replicates) exceeds the channel's own $f{=}0$
record-bootstrap 95th percentile ($R = 400$, $n$-matched). Confound check: the
eleven grid coordinates of the $f = 0.10$ mixture are $z$-scored against 200
host bootstraps; a tier passes iff $\max|z| < 3$.

\begin{table}[t]
\centering
\caption{Quotient-level spike-in recovery (fraction of six host channels) by
tier and mixture fraction, with the mixture-level confound check. Source:
\texttt{power13\_quotient\_spikein.csv}, \texttt{power13\_confound\_check.csv}.}
\label{tab:spikein}
\footnotesize
\setlength{\tabcolsep}{4pt}
\begin{tabular}{lcccccc}
\toprule
injection tier & $f{=}0.01$ & $f{=}0.05$ & $f{=}0.10$ & $f{=}0.25$ & $\max|z|$ (med/max) & clean hosts \\
\midrule
(a) naive & 0.50 & 1.00 & 1.00 & 1.00 & 15.8 / 21.5 & 0/6 \\
(b) magnitude-matched & 0.50 & \textbf{1.00} & \textbf{1.00} & 1.00 & \textbf{1.8 / 6.5} & 5/6 \\
(c) base-matched adversarial & 0.00 & \textbf{1.00} & \textbf{1.00} & 1.00 & \textbf{2.0 / 2.9} & \textbf{6/6} \\
\bottomrule
\end{tabular}
\end{table}

The earlier off-grid design (exact products into rounded hosts) drifts the
mixture's grid coordinates at $|z|$ up to $10^7$ and is retained only as an
illustration of why the confound check is mandatory.

\paragraph{Count-kind hosts (v10.3, exploratory; seed 20260719).}
The tier-(b) in-place design was extended to count-kind hosts
(\path{stage26_counthosts.py}, host recipe and holds-rule frozen in
\path{run_config_count26.json}; outputs \path{count26_*.csv}). The
frozen magnitude screen (median $\ge 10^5$, $\ge 500$ eligible cores)
selects three telemetry byte-count channels from distinct families---the
only count-kind channels at the required magnitude, which itself scopes the
claim. Recovery: $0/3$ at $f = 0.01$, $3/3$ at $f = 0.05$ and above
(replicate-median $\keff^{\mathrm{core}}$ against each channel's own
$f{=}0$ bootstrap 95th percentile, $R = 200$). The mixture-level confound
check exceeds the $|z| < 3$ bar in all three hosts (max $|z|$ $3.3$--$5.2$),
so per the frozen rule the extension does \emph{not} qualify as clean
recovery; the per-coordinate decomposition, however, shows every flagged
coordinate is a \emph{residue} score drifting \emph{negative}
(tv$_{100}$, tv$_{25}$, tv$_{47}$, tv$_{43}$) with the decimal-grid
coordinates (grid mass, depth, conformance, $c_2$, $c_5$) within noise: the
injections dilute the hosts' strong intrinsic resonance, the same mechanism
as the one flagged amount-kind host, not grid leakage. Both the recovery and
the flags are reported, and Section~7 of the main text is scoped
accordingly.

\paragraph{Power curves and false-positive calibration (v10.3; seed
20260721).} Assembled from the frozen power13 outputs without recomputation
(\path{stage28_powerfp.py}; outputs \path{powerfp28_curves.csv},
\path{powerfp28_fpcal.csv}): per-tier recovery is $0.5$, $1.0$, $1.0$, $1.0$ (naive and
magnitude-matched) and $0.0$, $1.0$, $1.0$, $1.0$ (adversarial) of six hosts
at $f = 0.01$, $0.05$, $0.10$, $0.25$, with per-host effect sizes in units of
each channel's own noise band. False-positive calibration is by construction
of the record-bootstrap band (nominal $0.05$); the single frozen $f{=}0$
observation per host sits below its threshold in $6/6$ hosts, and the
count-host extension uses the same construction.

\section{Pre-registration ledger and misfire postmortems}
\label{s:prereg}

\begin{table}[t]
\centering
\caption{All twenty frozen decision rules with outcomes. Source:
\texttt{artifact/manifests/decision\_rules.csv}.}
\label{tab:prereg}
\scriptsize
\begin{tabular}{llp{0.44\linewidth}c}
\toprule
run & id & rule (frozen) $\to$ outcome & verdict \\
\midrule
gate07  & G1 & product AUC $\ge0.85$ $\to$ $0.86$--$0.96$ & met \\
gate07  & G2 & one digit of rounding destroys detection $\to$ chance at grid $100$ & met \\
hunt08  & H8-1 & structured products AUC $\ge0.85$ $\to$ $0.889$--$0.998$ & met \\
hunt08  & H8-2 & prime-pair $\keff\approx1.1$ $\to$ $1.035$ & met$^{\dagger}$ \\
hunt09  & H9-1 & residual $\to0$ under core-magnitude null $\to$ $-0.0184{\to}{-}0.0001$ & met \\
hunt09  & H9-2 & COD multiplicity $\keff<1$ $\to$ $0.534$ & met \\
hunt09  & H9-3 & NIST $\keff\ne1$ (direction uncertain) $\to$ $1.707$ & met \\
hard10  & H10-1 & semiprime: $\keff$ blind, full-profile sees $\to$ $0.44$/$0.93$ & met \\
hard10  & H10-2 & off-grid spike-in recovered $\to$ $6/6$ & met \\
hard10  & H10-3 & $n{\to}n{+}1$ collapses detection $\to$ AUC $0.44$ & met \\
hard10  & H10-4 & grid coordinates beat Benford on grid mismatch $\to$ $1.00$ vs $0.46$ & met \\
emp11   & E11-1 & employment multiplicative null $\to$ $\keff\,0.98$--$1.00$ & met \\
emp11   & E11-2 & survey grid-marked vs census $\to$ $\rmass\,0.474$ vs $0.102$ & met \\
\textbf{whisp12} & \textbf{W12-1} & replicate-or-retire whisper $\to$ no CI-clean replication & \textbf{missed} \\
power13 & P13-1 & quotient spike-in powered $\to$ $6/6$ (adversarial clean) & met \\
\textbf{power13} & \textbf{P13-2} & energy omnibus recovers pairs $\to$ underpowered ($0.17$) & \textbf{missed} \\
\textbf{power13} & \textbf{P13-3} & atom count decreases $\to$ direction inverted & \textbf{missed} \\
power13 & P13-4 & grid coordinates add value on subtle grid $\to$ $1.00$ vs $\le0.53$ & met \\
vote14  & V14-1 & votes multiplicative null $\to$ $\keff\,0.98$--$1.03$ & met \\
vote14  & V14-2 & votes vs modeled CVAP grid-marked $\to$ $\rmass\,0.275$ vs $0.12$ & met \\
\bottomrule
\end{tabular}

{\footnotesize $^{\dagger}$The H8-2 expectation was stated qualitatively in
the frozen text (``$\approx 1.1$''); the recorded verdict applied the run's
own criterion (elevated above $1$ with detection AUC near chance), which
$1.035$ met. No quantitative tolerance was frozen; we state this rather than
imply one.}
\end{table}

\paragraph{Epistemic status of the registrations.} The decision rules were
frozen in configuration files inside the analysis tree (hash-integrity via
the artifact manifests), not lodged with an external registry, so they are
\emph{internally frozen} rather than externally timestamped; readers should
weight them accordingly. Two further distinctions matter. First, the
acquisition-frozen runs (emp11, whisp12, vote14) wrote their rules before
any network fetch, so those rules were evaluated on data the authors had
never seen; the computation-frozen runs (gate07, hunt08, hunt09, hard10,
power13) wrote their rules before the computation but over corpus data that
existed locally during rule development. Second, seed values follow a
date-like labeling convention ($20260702, 20260707, \dots$); they are
labels, not timestamps, and carry no registration force of their own
(\S S9). The v10.3 exploratory extensions follow the same
internal-freeze protocol and are labeled exploratory throughout.

\paragraph{P13-2, the underpowered omnibus.}
Energy distance to a fixed generic reference cloud was pre-registered as the
primary statistic for balanced-pair injections ($\ge 4/6$ channels at
$f \le 0.10$); it recovered at most $0.17$. Cause: dilution---a real host
already sits far from a generic cloud, so a small injected fraction barely
moves the group statistic. The targeted stripped-core statistics recover
$6/6$ at $f = 0.05$. Implication: power lives in targeted core statistics
keyed to the specific alternative; a fixed reference cloud is the wrong null
for an off-cloud channel.

\paragraph{P13-3, the inverted direction.}
The mean atom count of the stripped core was pre-registered to decrease under
balanced-pair injection (intuition transferred from a synthetic null with
many-part comparators). On real hosts the direction inverts: real cores
average ${\approx}1.1$ atoms, so two-atom injections \emph{raise} the count.
Correct arithmetic against the wrong baseline; the conclusion rests on
$\keff^{\mathrm{core}}$ and tail statistics, whose directions held.
Implication: coordinate directions must be calibrated on the real host
baseline.

\paragraph{W12-1, the vanishing whisper.}
A candidate multiplicative residual in preliminary model-based survey
estimates (scale-clean first log-share residual $dL_1' = +0.016$) was registered for promotion only if it
replicated CI-clean, same sign, effect $\ge 0.01$, in an independent
estimation system. Across four systems (CES real-time vintages, PEP, seasonal
adjustment, ACS) the sign was unstable and no contrast was CI-clean; the
signal existed only in the preliminary vintage and vanished after
benchmarking---itself an instance of the recording heuristic: benchmarking is
a later additive re-anchoring that severs multiplicative structure. The rule
correctly retired the candidate; sub-$0.02$ multiplicative residuals in survey
estimates are estimation-model transients outside the instrument's envelope.

\section{Exact-integer catalogue and computation}
\label{s:exact}

\paragraph{Catalogue.}
Synthetic ground truth (magnitude- and moment-matched): sums and Poisson
tallies $\keff = 1.00$ exactly; products of $k$ factors AUC $0.86$--$0.96$;
detection survives factor imbalance to a $90/10$ log-split and is destroyed by
one digit of rounding. Structured products with closed-form factorizations
(magnitudes to $10^{7263}$): factorials, binomials, multinomials, primorials,
$B$-smooth numbers, and finite-group orders (e.g.\
$|GL(k,q)| = q^{k(k-1)/2} \prod_{i=1}^k (q^i - 1)$) all clear the
pre-registered AUC $\ge 0.85$ bar ($0.889$--$0.998$). Measured fields:
crystallographic site multiplicities~\citep{coddb} $\keff = 0.534 \pm 0.091$
($n = 11{,}240$), atomic degeneracy products~\citep{nistasd} $1.707 \pm 0.557$ ($n = 505$),
graph automorphism orders~\citep{snap} exact to $10^{17{,}265}$ with
$\keff$ up to $4.44$;
real additive fields $0.996$. Balanced prime pairs are the edge case:
$\keff$-blind asymptotically (for distinct primes $p, q$,
$H_2 = \tfrac12 + 2(\ell_1 - \tfrac12)^2 > \tfrac12$ strictly, meeting the
null only in the magnitude limit) yet recoverable from full-profile statistics
at AUC $0.83$--$0.93$.

\paragraph{Exact computation.}
No value above the sieve range is factorized by trial division, and no profile
is computed through floating point. Exponent maps come in closed form:
Legendre's $v_p(n!) = \sum_{k\ge1} \lfloor n/p^k \rfloor$ for
factorials~\citep{legendre1808}; Kummer's carry count for
binomials/multinomials~\citep{kummer1852}; closed factorization of group
orders; twin-class reduction plus Schreier--Sims for automorphism
orders~\citep{seress2003}.
Arbitrary-precision arithmetic certifies residual large factors; the only
floating-point step is $\ln n = \sum_i a_i \ln p_i$ from the exact exponent
map. There is no path by which float overflow could manufacture the reported
$\keff$ values.

\section{Benchmarks: digit battery versus grid coordinates}
\label{s:bench}

\begin{table}[t]
\centering
\caption{Attribution vs.\ detection: naive digit battery (incl.\ the
Beber--Scacco vote-forensic test) vs.\ grid coordinates, by contrast (AUC;
ties retained). Source: \texttt{power13\_naive\_benchmark.csv},
\texttt{vote14\_benchmark.csv}.}
\label{tab:naive}
\footnotesize
\setlength{\tabcolsep}{4pt}
\begin{tabular}{p{4.1cm}p{1.9cm}p{1.6cm}cp{1.6cm}}
\toprule
contrast & terminal-digit battery & Beber--Scacco & grid coords & role \\
\midrule
survey vs.\ census, employment (decimal grid) & 1.00 & --- & 1.00 (tie) & calibration \\
ACS point estimates vs.\ census & 0.29--0.54 & --- & 0.77 & below bar \\
ACS margin-of-error vs.\ census & 0.74--1.00 & --- & 1.00 (tie) & attribution \\
enumerated votes vs.\ modeled CVAP (5-grid) & 1.00 & fires on CVAP & 1.00 (tie) & attribution \\
real-return fabrication contrast (2-sided) & \textbf{1.00} & anti-detects & 0.68--0.83 & detection lost \\
constructed 47-tick vs.\ 43-tick & $\le$0.53 & --- & \textbf{1.00} & detection \\
era-mixture fabrication & 0.46--0.74 & --- & 0.49 (both fail) & neither \\
\bottomrule
\end{tabular}
\end{table}

(Dashes in the Beber--Scacco column are N/A by design: the test is defined
for election-return-style count series and was run only on the contrasts
involving them.) Two readings of the fabrication row, both reported: under the frozen one-sided
orientation the grid coordinates ``add value'' at $f = 0.25$ because the
one-sided digit battery anti-detects; read two-sided, a last-two-digit drift
test reaches AUC $1.00$ and dominates. On real returns the grid coordinates
add detection value nowhere; their detection edge lives on non-decimal grids
(constructed case), and their real-data role is attribution.

\section{Artifact, manifests, and reproduction}
\label{s:artifact}

The deposit contains: the $21$ frozen v8-era configuration files
(\texttt{run\_config\_*}) plus the exploratory geo15 and six v10.3 configs;
the decision-rule manifest (20 rules); \texttt{claim\_manifest.csv} (36
claims, each mapped to script, output table/figure, config, and SHA-256);
the deviation log (16 entries); all analysis scripts (stages 1--21, plus the
exploratory \texttt{stage22\_geo15.py} with unit tests) and figure scripts
(\texttt{scripts\_v10/}); hash manifests for tables and figures; and a worked
end-to-end verification of the CVAP $\chi^2$ claim in the README. Seeds
follow the per-build convention \texttt{2026070X}--\texttt{202607XX}
recorded in each config; the geo15 build uses 20260715 and the v10.3
exploratory stages use 20260716--20260721. Seed values are date-like
\emph{labels} chosen for readability, not timestamps, and carry no
registration force. The v10.3 additions comprise
\path{stage23_loso.py} through \path{stage28_powerfp.py}, one frozen
config per stage (\path{run_config_loso23.json} \ldots{}
\path{run_config_powerfp28.json}), and outputs prefixed
\path{loso23_}, \path{taskpos24_}, \path{flat25_}, \path{count26_},
\path{gate27_}, \path{powerfp28_} in \path{tables/}; each plan was frozen
before its computation. \texttt{RESULT\_PROVENANCE.md} maps every
number retained in the main text to its output file and verification status.
Table~\ref{tab:displayprov} maps every main-text display to its generating
script and source tables.

\begin{table}[t]
\centering
\caption{Display provenance: every main-text figure and table, its
generating script (\texttt{scripts\_v10/}), and its source tables. ``artifact
hash'' means the table is covered by the frozen
\texttt{artifact/hashes/SHA256SUMS} or \texttt{claim\_manifest.csv};
``ledger hash'' means its SHA-256 is recorded in
\texttt{RESULT\_PROVENANCE.md}; geo15 tables are exploratory outputs of
\texttt{stage22\_geo15.py} (seed 20260715).}
\label{tab:displayprov}
\scriptsize
\setlength{\tabcolsep}{4pt}
\begin{tabular}{llp{0.45\linewidth}l}
\toprule
display & script & source tables & hash coverage \\
\midrule
Fig.~1 & \texttt{fig1\_cvap.py} & \texttt{vote14\_panel.csv}, \texttt{vote14\_beber\_scacco.csv}, \texttt{vote14\_grid\_probe.csv} & artifact \\
Fig.~2 & \texttt{fig2\_geography.py} & \texttt{geo15\_geography\_channel.csv}, \texttt{geo15\_controlled.csv} & geo15 (exploratory) \\
Fig.~3 & \texttt{fig3\_waterfall.py} & \texttt{derounding\_effect.csv}, \texttt{deepstrip\_effect.csv}, \texttt{hunt09\_residual\_rebaseline.csv}, \texttt{resonance\_controls.csv}, \texttt{residue\_structure.csv} & artifact + ledger \\
Fig.~4 & \texttt{fig4\_mechanism\_power.py} & \texttt{hard10\_degradation.csv}, \texttt{power13\_quotient\_spikein.csv} & artifact \\
Fig.~5 & \texttt{fig5\_acs.py} & \texttt{whisp12\_acs.csv} & artifact \\
Fig.~6 & \texttt{fig6\_exact.py} & \texttt{gate\_rungs.csv}, \texttt{hunt09\_lowkeff.csv}, \texttt{hunt09\_highkeff.csv}, \texttt{family\_profiles\_v3.csv} (restricted to the $367$ frozen families), \texttt{observational\_corpus\_v2.csv} & artifact \\
Table~1 & --- & \texttt{family\_inventory.csv} (frozen corpus composition) & artifact \\
Table~2 & --- & \texttt{hunt09\_residual\_rebaseline.csv} and the frozen driver tables (\texttt{derounding\_effect.csv}, \texttt{deepstrip\_effect.csv}, \texttt{residue\_structure.csv}) & artifact + ledger \\
Table~3 & --- & none (interpretive summary; no numeric claims) & --- \\
\bottomrule
\end{tabular}
\end{table}

\section{Operational protocol and gate validation}
\label{s:protocol}

\paragraph{The two-step gate, operationally.}
\emph{Inputs:} the flagged integer partition and a clean reference partition
(or the magnitude-matched uniform null below). \emph{Step 1:} run the digit
test that raised the concern; record its statistic and screen (e.g.\
Beber--Scacco $\chi^2_9$ on records $\ge 1000$). \emph{Step 2:} compute the
recording-grid coordinates. Defaults, as validated here: the modulus set $\{4$, $8$, $25$, $49$,
$100$, $47$, $43\}$; modal grid $g_0$, the
largest $g$ among $2$, $4$, $5$, $10$, $20$, $25$, $50$, $100$, $200$,
$250$, $500$, $1000$ with conformance $\ge 0.90$ (else $1$); magnitude-matched reference = uniform integers drawn
to the series' digit-length histogram ($20$ seeded draws; report excess =
observed minus null-mean TV); $z$-scores against the reference draws'
spread when a formal scale is needed. \emph{Multiplicity:} with $7$ moduli
and several partitions, treat single marginal excesses as screening only;
the validated flag is TV excess $\ge 0.05$ (an order of magnitude above the
generic level $\approx 0.006$) at any modulus, or $g_0 > 1$.
\emph{Stop/go:} flag present $\to$ report ``the alarm is grid-compatible''
and seek the documented recording rule (attribution requires the
documentation); flag absent $\to$ ``not attributable to a grid this
instrument can see''---substantive investigation proceeds. The output is
never a verdict on the data. A worked verification script for the CVAP row
ships in the deposit README.

\paragraph{Worked CVAP report (every field of the main-text protocol).}
Unit of analysis: county tabulation ($3{,}222$ county-level rows in the
special tabulation; the ACS/decennial county frame of main-text Figure~5 has
$3{,}144$; $3{,}171$ rows pass the $\ge 1000$ screen). Scored population: published \texttt{CVAP\_EST},
2018--2022 special tabulation. Representation: last digits (step 1);
recording-grid coordinates (step 2). Baseline: last-digit uniformity;
magnitude-matched uniform null. Known recording rule: the documented rounding maps estimates of $1$--$7$
to $4$ and rounds estimates $\ge 8$ to the nearest five, so every analyzed
value (all $\ge 1000$) lies in the nearest-five regime and the five-grid
statement is exact for the analyzed data \citep{cvaptechdoc}. Result class: construction-attributed (signature
$+$ documentation). Detector outcome: $\chi^2_9 = 12{,}684$, $p$ below
reporting precision. Gate outcome: $g_0 = 5$; TV excess $+0.765$ at modulus
$25$, $+0.729$ at $100$. Compatible alternative mechanisms: none required
beyond the documented rule. Licensed conclusion: the alarm is attributable
to the documented five-grid. Not licensed: any statement about the accuracy
or integrity of the underlying tabulation.

\paragraph{Adversarial co-occurrence example (v10.3, seed 20260720).}
Fabricated \emph{and} gridded: values drawn from a smooth lognormal
generator (``fabricated'': no real process behind them), then published on a
five-grid, fire the last-digit test at $\chi^2_9 \approx 11{,}800$ and show
$g_0 = 5$ with TV excess $+0.76$ at modulus $25$---the gate correctly
reports grid-compatible, because the \emph{alarm} is caused by the grid.
The example operationalizes the warning: the gate attributes the alarm, not
the data; a fabricated series published on a grid passes the gate exactly
like an authentic one.

\paragraph{Ground-truth validation library (v10.3, seed 20260720).}
Recipe frozen in \path{run_config_gate27.json}; output
\path{gate27_library.csv}. Sensitivity is computed over \emph{seven}
grid-truth series: the three documented real-data series (CVAP, CES, ACS
margin-of-error) plus four constructed ones (the fabricated-and-gridded
synthetic of the preceding paragraph, the binary-aligned allocation demo,
and the $47$- and $43$-tick re-quantizations). Coordinate sets: the corpus
instrument's eleven coordinates use five residue moduli
($100, 25, 49, 47, 43$); the operational default here extends the set to
seven (adding $4$ and $8$ for binary grids).
Documented-grid series: CVAP county (flagged, $g_0{=}5$); CES survey
employment, hundreds-grid (flagged, $g_0{=}100$, TV excess $+0.92$); ACS
margin-of-error (\textbf{missed}: its partial rounding sits below the
$0.05$ coarse threshold and $0.90$ conformance bar---this is the case that
requires the CI-based grid-mass comparison of the main text); binary-aligned
allocations (flagged, $g_0{=}4$); constructed $47$- and $43$-ticks (flagged
at their own moduli with $g_0{=}1$---the non-decimal capability). Non-grid
series: county returns 2020/2024, decennial-style county population counts,
additive synthetic sums, uniform null (all clean); NC precinct returns
(\textbf{false-flagged} at modulus $8$, excess $+0.116$)---a small-magnitude
series in exactly the failure regime named by the flatness stress of
\S S2. Sensitivity $6/7$ (the one miss is a documented real series);
specificity $5/6$; both misses mechanistically explained. The library doubles as the validation table for the main-text
protocol; its scope is series already cached by the project---no new
acquisition.

\bibliographystyle{plainnat}
\bibliography{references_v10}

\end{document}
